### 2017-08-24 Paper01_EnthalpyAndCrystallization.tex
Results - Dynamic XRD - started filling draft and data table.

>>>>

When looking at the dynamic \gls{xrd} data it can been seen that many phases seen in the bulk fail to nucleate or are not observed as strongly in the film. A Mg and Mg$_{51}$Zn$_{20}$ peak at 32.1\degree~ is first clearly seen in the bulk at a temperature of 170\degree C. In the film there is first clear evidence of this peak at 90\degree C, although its resolution is poor from 150-170\degree C.

In the bulk a double peak at 38\degree~ and 39\degree~ begins emerge at 125\degree C, phases which never evolve in the film. The bulk peaks at 42.3\degree~ and 43.7\degree~ start to emerge at 165\degree C but are never seen in the film.

\begin{table}[h]
	\centering
	\begin{tabular}{ c c c c c c c c }
		\toprule
		Peak & Bulk & Film & Change & Bulk Start & Film Start & Change & Phases \\
		& $2\theta$ & $2\theta$ & \% & \degree C & \degree C & \% & at\% \\
		\midrule
		1    & 32.1 & 32.1 & 0.0\%  & 170 & 90 & -47.1\% & Mg, \MgZn \\
		2    & 34.3 & 34.3 & 0.0\%  & 75  & 115 & 53.3\% & Mg, \MgZn, \CaMgZnFive \\
		3    & 36.6 & 36.5 & -0.3\% & 130 & 130 & 0.0\%  & Mg, \MgZn \\
		4    & 38.0 & N/A  & N/A    & 125 & N/A & N/A    & \MgZn, \CaMgZnFive \\
		5    & 39.0 & N/A  & N/A    & 125 & N/A & N/A    & \MgZn \\
		6    & 42.3 & N/A  & N/A    & 165 & N/A & N/A    & \CaMgZnFive \\
		7    & 43.7 & N/A  & N/A    & 170 & N/A & N/A    & \CaMgZnFive \\
		8    & 47.7 & 47.6 & -0.2\% & 170 & 170 & 0.0\%  & Mg, \MgZn \\
		9    & 53.3 & N/A  & N/A    & 175 & N/A & N/A    & \MgZn, \CaMgZnFive \\
		10   & 57.2 & N/A  & N/A    & 170 & N/A  & N/A   & Mg, \MgZn \\
		\bottomrule
	\end{tabular}
	\caption{Main dynamic \gls{xrd} peaks for both the bulk and the film. Data shows minor shifting for peaks 3 and 8, large state temperature differences for peaks 1 and 2, failure of peaks $4-7$, 9, and 10 to nucleation in the film.}
	\label{tab:Dynamic_XRD}
\end{table}
